\input{header.tex}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{vmargin}
\usepackage{indentfirst}
\usepackage{titling}
\usepackage{color} 
\usepackage{siunitx}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[backend=biber,backref=true,style=unsrt,
style=numeric-comp,block=ragged,firstinits=true]{biblatex}

%macro for column vector notation
\makeatletter
\newcommand{\Spvek}[2][r]{%
  \gdef\@VORNE{1}
  \left(\hskip-\arraycolsep%
    \begin{array}{#1}\vekSp@lten{#2}\end{array}%
  \hskip-\arraycolsep\right)}

\def\vekSp@lten#1{\xvekSp@lten#1;vekL@stLine;}
\def\vekL@stLine{vekL@stLine}
\def\xvekSp@lten#1;{\def\temp{#1}%
  \ifx\temp\vekL@stLine
  \else
    \ifnum\@VORNE=1\gdef\@VORNE{0}
    \else\@arraycr\fi%
    #1%
    \expandafter\xvekSp@lten
  \fi}
\makeatother

\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}


\title{Condensed Matter Physics II}
\subtitle{Suggested material for class exercise sessions}
\date{Spring 2015}

\begin{document}


\maketitle

\setlength{\unitlength}{1cm}
%\advance\textwidth by 3cm
%\advance\hoffset by -1.5cm 
\advance\textheight by 1cm
\advance\voffset by -1.5cm
\setmarginsrb{3cm}{0.5cm}{1.5cm}{1cm}{1cm}{1cm}{1cm}{1cm}
%\setlength{\parindent}{0cm}%

\pagestyle{plain}

\section{Group theory}

\begin{itemize}
\item Marder, p222 and others
\item Check out Wolfram book.
\item ETH pb 3.1
\end{itemize}

\section{Band calculation in empty lattice}

\begin{itemize}
\item Pb set \#2 from ETH, CMI folder.
\end{itemize}

\section{Semi conductor physical quantities}

\begin{itemize}
\item Nice exercise on computation of specific heat of a semi
  conductor in Pb set \#6 from ETH, CMI folder. Goes together with
  computation of specific heat of metals, done in CMI: ex. 6.1.b and
  6.1.c
\item same as above with Pauli susceptibility, maybe less interesting,
  6.2.b and 6.2.c from ETH.
\item ETH \# 10.2: Reflectivity of simple metals and Semiconductors.
\item UC Davis 140B MT1
\item UC Davis 140B P3
\end{itemize}

\section{Impurities in semi conductors}

\begin{itemize}
\item CMI Arizona 460, prob9, Arizona 472 Pb6
\end{itemize}

\section{Donor states in Si}

\begin{itemize}
\item CMI Arizona 472, prob7
\end{itemize}


\section{Conductivity tensor}

\begin{itemize}
\item Pb set \#12 from ETH, CMI folder.
\item UCSD: graphene, reciprocal lattice, band
  insulator. https://physics.ucsd.edu/~wucj/teach/Phy152A_2011/phy152A.html
\item Chap 9 of Jarrell in CMI, transport.
\item Chap 11 Jarrell dielectric.
\item Chap 12 Jarrell semi-con
\item check vvdensky folder with prob set and sol
\end{itemize}

\section{Misc}
\begin{itemize}
\item Wizman tuto in CMI, on Hall effect, and reflectivity.
\item UC Davis 140B P2,P3 for dielectric function and index of
  refraction
\item lattice exercises UC Davis 240A P1
\end{itemize}

Arizona: http://www.physics.arizona.edu/~stafford/Courses/

\end{document}
