\input{header.tex}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{vmargin}
\usepackage{indentfirst}
\usepackage{titling}
\usepackage{color} 
\usepackage{siunitx}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[backend=biber,backref=true,style=unsrt,
style=numeric-comp,block=ragged,firstinits=true]{biblatex}
\addbibresource{ref-notes.bib}
\bibliography{ref-notes}
\graphicspath{{plot_synthesis/} {Feynman/}}

\newcommand{\mastersig}{\ensuremath{\Im{\widehat{\Sigma}^{A,B}(k,E)}}\xspace}
\newcommand{\chiqw}{\ensuremath{\Im{\chi}(q,\omega)}\xspace}

\providecommand{\norm}[1]{\lVert#1\rVert}

\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

\title{Condensed Matter II}
\subtitle{Problem set \#8}
%\author{}
\date{Spring 2014}

\begin{document}

\maketitle

\setlength{\unitlength}{1cm}
%\advance\textwidth by 3cm
%\advance\hoffset by -1.5cm 
\advance\textheight by 1cm
\advance\voffset by -1.5cm
\setmarginsrb{3cm}{0.5cm}{1.5cm}{1cm}{1cm}{1cm}{1cm}{1cm}
%\setlength{\parindent}{0cm}%

\pagestyle{plain}

\section*{Donor impurities in GaAs}

\subsection*{Background}

We consider the direct band gap semiconductor GaAs, with $N_d = 10^{16}.\text{cm}^{-3}$
hydrogenic donor impurities. The following properties are
given:

\begin{itemize}
\item direct band gap: $E_g = 1.40$ eV.
\item $m^*_e = 0.07 m_0$ for the conduction band effective mass.
\item $m_{h} = 0.7 m_0$ for the valence band holes effective mass.
\item $\epsilon_{\text{GaAs}} = 15$
\end{itemize}

\subsection*{Questions}

\subsubsection*{Temperature dependence of the Fermi level}

\begin{enumerate}[label=(\roman*)]
\item Compute the concentration of intrinsic carriers in the material,
  and compare it with the concentration of impurities.
\item Compute the ionization energy $E_d$ of the impurities.
\item Establish the expression of the density of carriers, as a
  function of $T, E_d, N_d, E_F$.
\item From the previous expression, deduce the temperature dependent
  expression of $E_F(T)$. Compute $E_F(T)$ fot $T=300$K and $T=30$K.
\end{enumerate}

\subsubsection*{Transport properties}

\begin{enumerate}[label=(\roman*)]
\item Compute the electron and hole carrier concentrations at room
  temperature and at $30$K.
\item What is the critical doping, above which an impurity band
  would appear as a result of the presence of substitutional
  impurities in GaAs? What is the main difference between the impurity
  band scenario and the the isolated impurity scenario?
\end{enumerate}



%\section

\end{document}