\input{header.tex}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{vmargin}
\usepackage{indentfirst}
\usepackage{titling}
\usepackage{color} 
\usepackage{siunitx}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[backend=biber,backref=true,style=unsrt,
style=numeric-comp,block=ragged,firstinits=true]{biblatex}
\addbibresource{ref-notes.bib}
\bibliography{ref-notes}
\graphicspath{{plot_synthesis/} {Feynman/}}

\newcommand{\mastersig}{\ensuremath{\Im{\widehat{\Sigma}^{A,B}(k,E)}}\xspace}
\newcommand{\chiqw}{\ensuremath{\Im{\chi}(q,\omega)}\xspace}

\providecommand{\norm}[1]{\lVert#1\rVert}

\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

\title{Condensed Matter II}
\subtitle{Problem set \#9}
%\author{}
\date{Spring 2014}

\begin{document}

\maketitle

\setlength{\unitlength}{1cm}
%\advance\textwidth by 3cm
%\advance\hoffset by -1.5cm 
\advance\textheight by 1cm
\advance\voffset by -1.5cm
\setmarginsrb{3cm}{0.5cm}{1.5cm}{1cm}{1cm}{1cm}{1cm}{1cm}
%\setlength{\parindent}{0cm}%

\pagestyle{plain}

\section*{Hall effect}

\subsection*{Isotropic semiconductor}

In this section, we study the Hall coefficient in a
semiconductor in the presence of both hole and electron charge carriers:

\begin{itemize}
\item electron density $n_e$
\item hole density $n_h$
\item electron mobility $\mu_e$
\item hole mobility $\mu_h$
\end{itemize}

\begin{enumerate}[label=(\roman*)]
\item Assuming $B=0.1$ T and $m^* = m_0$, What is the critical relaxation
  time $\tau_c$ below which the weak magnetic field approximation is valid?
\item Assuming $\mu_e = 1000 \text{ cm}^2/V.s$, is this approximation valid?
\item Derive the expression of the Hall coefficient in the material.
\end{enumerate}

\subsection*{Anisotropic case}

In this section a single kind of charge carriers (electrons) is
present, but its effective mass tensor is
anisotropic.

Consider a degenerate
n-type material with $10^{17}$ electron carriers per cm$^3$ in the
conduction band. The electrons occupy conduction states associated
with the 6 electron carrier pockets of
Si. Such carrier pockets are characterized by the mass components
$m_t = 0.19 m_0$ and $m_l = 0.98 m_0$.

Assume $\vec{B}$ is along the $z$ axis, $\vec{j}$ is along the $x$
axis, and the relaxation time is $\tau$.

\begin{enumerate}[label=(\roman*)]
\item By analogy with the derivation in the isotropic case, establish the
  expression of the contribution of one electron pocket to the
  conductivity tensor.
\item Express the Hall coefficient as a function of the components of
  the conductivity tensor, and B.
\item Assume the weak field approximation is valid, and deduce the
  expression of the Hall coefficient as a function of the effective
  masses, and of the isotropic Hall coefficient.
\item Derive the expression of the transverse magnetoresistance, and
  comment on its magnitude.
\end{enumerate}

%\section

\end{document}